Demes: a standard format for demographic models

### 2022-08-09 paper.tex

% local definitions
\newcommand{\ms}[0]{\texttt{ms}}
\newcommand{\msprime}[0]{\texttt{msprime}}
\newcommand{\stdpopsim}[0]{\texttt{stdpopsim}}
\newcommand{\demes}[0]{\texttt{demes}}
\newcommand{\demesdraw}[0]{\texttt{demesdraw}}
\newcommand{\Demes}[0]{\texttt{Demes}}
\newcommand{\moments}[0]{\texttt{moments}}
\newcommand{\dadi}[0]{\texttt{dadi}}
\newcommand{\fwdpy}[0]{\texttt{fwdpy11}}
\newcommand{\slim}[0]{\texttt{SLiM}}
\newcommand{\gadma}[0]{\texttt{GADMA}}
\newcommand{\tskit}[0]{\texttt{tskit}}
\newcommand{\MSMC}[0]{\texttt{MSMC}}
\newcommand{\demesslim}[0]{\texttt{demes-slim}}

@@

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Ryan N. Gutenkunst}
\author[4]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[8]{Stephan Schiffels}
\author[3]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\aleph$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison}
\affil[3]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[4]{Institute of Ecology and Evolution, The University of Edinburgh}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California, Irvine}
\affil[8]{Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

@@

\section*{Acknowledgments}
We would like to thank the editor and reviewers for helpful
comments that have significantly improved this manuscript.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Ryan Gutenkunst and Travis Struck were supported by the National Institute of General Medical Sciences of the National Institutes of Health (R01GM127348 to RNG).
Matthew Hartfield is supported by a NERC Independent Research Fellowship (NE/R015686/1).
Jerome Kelleher is supported by the Robertson Foundation.
Stephan Schiffels was supported by funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (grant agreement No 851511).

>>>>

% local definitions
\newcommand{\ms}[0]{\texttt{ms}}
\newcommand{\msprime}[0]{\texttt{msprime}}
\newcommand{\stdpopsim}[0]{\texttt{stdpopsim}}
\newcommand{\demes}[0]{\texttt{demes}}
\newcommand{\demesdraw}[0]{\texttt{demesdraw}}
\newcommand{\Demes}[0]{\texttt{Demes}}
\newcommand{\moments}[0]{\texttt{moments}}
\newcommand{\dadi}[0]{\texttt{dadi}}
\newcommand{\fwdpy}[0]{\texttt{fwdpy11}}
\newcommand{\slim}[0]{\texttt{SLiM}}
\newcommand{\gadma}[0]{\texttt{GADMA}}
\newcommand{\gIMble}[0]{\texttt{gIMble}}
\newcommand{\tskit}[0]{\texttt{tskit}}
\newcommand{\MSMC}[0]{\texttt{MSMC}}
\newcommand{\demesslim}[0]{\texttt{demes-slim}}

@@

% Authors: please add your name and affiliation here, in alphabetical order.
% Second Authors
\author[3]{Gertjan Bisschop}
\author[4]{Ryan N. Gutenkunst}
\author[3]{Matthew Hartfield}
\author[5]{Ekaterina Noskova}
\author[8]{Stephan Schiffels}
\author[4]{Travis J. Struck}
%Senior Authors
\author[6,$\dagger$,$\aleph$]{Jerome Kelleher}
\author[7,$\dagger$]{Kevin R. Thornton}

\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison}
\affil[3]{Institute of Ecology and Evolution, The University of Edinburgh}
\affil[4]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California, Irvine}
\affil[8]{Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

@@

\section*{Acknowledgments}
We would like to thank the editor and reviewers for helpful
comments that have significantly improved this manuscript.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
Ryan Gutenkunst and Travis Struck were supported by the National Institute of General Medical Sciences of the National Institutes of Health (R01GM127348 to RNG).
Matthew Hartfield is supported by a NERC Independent Research Fellowship (NE/R015686/1).
Jerome Kelleher is supported by the Robertson Foundation.
Stephan Schiffels was supported by funding from the European Research Council (ERC) under the European Union’s Horizon 2020 research and innovation programme (grant agreement No 851511).
Gertjan Bisschop was supported by funding from the ERC(ModelGenomLand, 757648).

### 2022-08-09 software-table.tex
Fix build and trim MSMC text
Brackets for msmc url

@@

>>>>

\gIMble &
    Fits IM-type demographic models and infers genomic barriers to geneflow \citep{laetsch2022gimble}. Outputs inferred models in Demes format. \\

@@

\MSMC & A script provided in the MSMC-tools repository
(\url{https://github.com/stschiff/msmc-tools})
converts MSMC \citep{SchiffelsDurbin2014,WangSchiffels2020} output to the demes format. 
\\
